Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-08 conclusion.tex
tweak in Conclustion and Related work

%\TODO{more future work here?}
In the future, we plan to explore the intelligent job placement and routing configurations for diversified workloads running on the dragonfly network. The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload. We plan to collect workload traces from production system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration. We envision that effectiveness of such new placement and routing polices can be examined on a configurable dragonfly system.

>>>>

%\TODO{more future work here?}
In the future, we plan to explore the intelligent job placement and routing configurations for diversified workloads running on the dragonfly network. The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload. We plan to collect workload traces from a production HPC system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration. We envision that effectiveness of such new placement and routing polices can be examined in future on a configurable dragonfly system.
